Energy and the CES production function

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better labels on fitted graphs.

### Can fittedGraphNoCSP and fittedGraphCSP be combined into one function with an argument?
### Or can the data filtering happen outside and everything else be the same?
### Did you copy and paste to make one from the other?  That should be a sign...
fittedGraphNoCSP <- function(data){
  fittedGraphData <- 
    data %>% 
    select(Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest) %>%
    melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
         value.name = "value", variable.name = "variable") %>%
    mutate(label = paste(variable, energy)) %>%
    # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
    filter(label %in% c("iGDP With energy", "fittedExp With energy", 
                        "fitted With energy", "fitted Without energy")
    ) %>% 
    mutate(
      label = plyr::mapvalues(label, 
                              from = c("iGDP With energy",  "fittedExp With energy",
                                       "fitted With energy", "fitted Without energy"), 
                              to = c("GDP",  "Reference model",
                                     "With energy", "Without energy")),
      label = relevelFactor(factor(label), 
                            c("GDP", "Reference model", "Without energy", "With energy"))
    )

>>>>

### Can fittedGraphNoCSP and fittedGraphCSP be combined into one function with an argument?
### Or can the data filtering happen outside and everything else be the same?
### Did you copy and paste to make one from the other?  That should be a sign...
fittedGraphNoCSP <- function(data){
  fittedGraphData <- 
    data %>% 
    select(Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest) %>%
    melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
         value.name = "value", variable.name = "variable") %>%
    mutate(label = paste(variable, energy)) %>%
    # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
    filter(label %in% c("iGDP With energy", "fittedExp With energy", 
                        "fitted With energy", "fitted Without energy")
    ) %>% 
    mutate(
      label = plyr::mapvalues(label, 
                              from = c("iGDP With energy",  "fittedExp With energy",
                                       "fitted With energy", "fitted Without energy"), 
                              to = c("GDP",  "Ref. model",
                                     "w/ energy", "w/o energy")),
      label = relevelFactor(factor(label), 
                            c("GDP", "Ref. model", "w/o energy", "w/ energy"))
    )
